On Secure Delegation of SampBQP with a Classical Client

### 2020-02-02 qpip0.tex

\subsection{Parallel Repetition of the Measurement Subprotocol}

>>>>

\subsection{$\QPIP_0$ protocol for $\SampBQP$}
%Parallel Repetition of the Measurement Subprotocol

The following protocol is a $\QPIP_0$ protocol for $\SampBQP$

$\forall c\in\bbN$ Soundness = $O(T^{-c})$

Given inverse poly p(T), we can parameterize the protocol to have soundness p(T)

%	\label{ProtoQPIP1}

\begin{protocol}{$\QPIP_0$ for $\SampBQP$}
\label{proto:QPIP0samp}
\begin{enumerate}
    \item Verifier start with description of quantum circuit $C$, input string $x$ 
    \item Both verifier and prover start with a soundness parameter $\varepsilon$.
    \item Run $N=O(1/\varepsilon)$ copies of [[urmilla protocol]] of in parallel.  On the testing round, the verifier uniformly randomly pick one copy and Hadamard round and has all other copies as test round.
    \item Verified reject if any of the test round result is wrong. Otherwise, decode the Hadamard run desult and run \cref{ProtoQPIP1} on it
    . 
\end{enumerate}
\end{protocol}
